Attributions for Poverty in Post-Socialist Countries

### 2014-03-28 index.Rmd
added tables to presentation

# Attributions for Poverty in Post-Socialist Countries - Markus Kainu & Mikko Niemelä

@@

@@

| pdf-ouput | source code |
| ------------ | -------------- |
| [Article draft in .pdf](article2013.pdf) | [source](article2013.Rmd) |

@@

- [HSE Moscow - November 12, 2013](moscow2013/lcsr20131112.html)
- [Jatkokoulutusseminaari Turku November 7, 2013](turku2013/slidesTkuJatko20131107.html)
- [ESA Torino - August 29, 2013](torino2013/TorinoSlides2013_final.html)

# Misc links

- [Article code in github](https://github.com/muuankarski/attributions)
- [rustfare-package](http://markuskainu.fi/rustfare/) *- toolbox for R language for open welfare data from Russian Federation*
- [rOpenGov](http://ropengov.github.io/) *-  R Ecosystem for Open Government Data and Computational Social Science*
- [markuskainu.fi](http://markuskainu.fi) *- personal website*

-----

>>>>

---
title: "Attributions for Poverty in Post-Socialist Countries"
author: [Markus Kainu & Mikko Niemelä]
---

@@

### Misc analysis

| html-ouput | source code |
| ------------ | -------------- |
| [Comparing waves 2006 and 2011](compareWaves.html) | [source](compareWaves.Rmd) |
| [Exploring the macro level correlations](correlations.html) | [source](correlations.md) |

@@

[Article draft in .pdf](article2013.pdf)

@@

| html-ouput | source code |
| ------------ | -------------- |
| [slides](attrib_slides.html) | [source](attrib_slides.Rpres) |

---------
